A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3

### 2015-07-31 skeleton.tex
Fixed table format, done paper, changed contour in plot setting

\begin{abstract}
We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy (SMG) SMM\,J0939+8315 at $z$ = 2.221, using  
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
The underlying continuum emission toward the foreground radio galaxy 3C220.3, at $z$ = 0.685, is detected with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.42 mJy. 
Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (10.1\,$\pm$\,1.3)\,Jy\,km\,s\pmOne, we derive 
 a lensing- and excitation-corrected CO line luminosity of \Lp = (2.7\,$\pm$\,0.6) $\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling performed on the archival 1\,mm continuum emission. 
 This translates to a molecular gas mass of $M_\textrm{gas}$\,=\,(2.3\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun. 
Fitting the SED models to the (sub)-millimeter data of this SMG yields a rest-frame dust temperature of $T_\textrm{dust}$ = 
63.1$^{+1.1}_{-1.3}$\,K, a dust mass of $M_\textrm{dust}$ = (5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared luminosity of 
$L_\textrm{IR}$ = (9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,\Lsun, after correcting for lensing magnification.
Our comparative study 
of the intrinsic properties (\eg gas mass, dust mass, star formation rate, and surface densities) in SMM
J0939+8315 
and other high-redshift SMGs and type-2 quasars suggests that SMM\,J0939+8315 is a faithful representation of both populations. 
SMM\,J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase in the currently favored evolutionary link model.
\end{abstract}
\keywords{cosmology: observations --- galaxies: formation --- galaxies: high-redshift ---  galaxies: starburst --- submillimeter: galaxies}

@@

In this paper, we present the detection of \CO line emission toward the background SMG obtained with the Combined
Array for Research in Millimeter Astronomy (CARMA), which refines the redshift, and permits the study of the physical conditions in the ISM of SMM\,J0939 in great detail. We report the detection of the underlying continuum emission and place constraints on the SED of the foreground FR-II galaxy at mm wavelength ($\sim$\,104 GHz). Based on the magnification factor from our lens model, we infer intrinsic properties of SMM\,J0939 and thereby 
conclude this paper by comparing our findings to other similarly bright, strongly-lensed SMGs at $z$$\sim$\,2.

We adopt a standard $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km\,\,Mpc\pmOne\,\,s\pmOne, $\Omega_\textrm{M}$\,=\,0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
The luminosity distances at $z$\,=\,0.685 and $z$\,=\,2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
corresponds to 8.406 kpc at $z$\,=\,2.221, and 7.169 kpc at $z$\,=\,0.685.

@@

\section{Results}\label{sec:res}
%\subsection{New Results: Continuum Emission} 
\subsection{New Results: 3C220.3} 
Averaging over all line-free channels, we detect $\sim$\,9$\sigma$ continuum emission at an averaged frequency of $\nu_{cont}$\,=\,104.2106 GHz ($\sim$\,2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$\,1.7 mm) at $z$\,=\,0.685. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, we thus expect it to be the dominant source of the continuum emission (see \S \ref{sec:SEDFg} for details). The task {\sc imfit} is used to estimate the peak position of the continuum emission, where the flux density is S$_\nu$\,=\,4.93\,$\pm$\,0.31\,\,mJy\,\,beam\pmOne. From the continuum measurement, the deconvolved source size 
is (8\farcs4\,$\pm$\,1\farcs1)\,$\times$\,(4\farcs9\,$\pm$\,0\farcs6) at $-$53.8$\degr$, and the integrated flux density is 7.53\,$\pm$\,1.42\,\,mJy. An overlay image of the 104 GHz  
continuum emission with the 9 GHz continuum emission (H14) is shown in Figure~\ref{fig:cont}, demonstrating that the continuum 
emission is marginally resolved at the resolution of our observations. It is therefore plausible that non-thermal emission from the radio lobes and core of the foreground galaxy dominate the integrated flux 
density of the measured continuum. We discuss this further in Section \ref{sec:SEDFg}. \par
The frequency range of our observations covers the HCO$^+$(2\,\rarr\,1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,\rarr\,2$_{20}$) 
transition line emission in the foreground galaxy, at 
the redshifted frequencies of 105.86, 107.71, and 108.79\,\,GHz, respectively. We establish 3$\sigma$ upper limits employing a typical FWHM line width of 
$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurements in a sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}. This results in upper limits of $<$ 2.66\,\,Jy\,\,km\,\,s\pmOne\ on the integrated emission line strengths.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel.pdf}
\caption{Left: Contour map of the 104 GHz continuum emission in the foreground radio galaxy 3C220.3. 
The contour levels start at $\pm$2$\sigma$, where $\sigma$ = 0.5 mJy beam\pmOne, and 
increment at steps 
of $\pm$2$\sigma$. 
The beam size is 12\farcs0\,$\times$\,6\farcs5, at P.A.\,=\,
$-$56$\degr$, as indicated in the bottom left corner. Right: CARMA 104 GHz continuum emission (red contours) overlaid on the VLA 9 GHz continuum emission (green contours and grayscale; H14). 
The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A. 
76$\degr$. The contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$, where $\sigma$\,=\,0.064 mJy beam\pmOne, and increment at steps of $\pm$2$^n\sigma$, 
where $n$ is a positive integer.
The central cross on each image indicates the position of the radio core of 3C220.3. \label{fig:cont}}
\end{figure*}
%\subsection{New Results: \CO Line Emission}
\subsection{New Results: SMM\,J0939\\ \CO Line Emission}
We detect \CO line emission at $\sim$\,8$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
The spatial extent of this SMG is $\sim$\,5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum in Figure~\ref{fig:mom0}; as such, 
the detected \CO line emission is spatially unresolved. We therefore extract the line profile (Figure~\ref{fig:mom0}) at the peak position of the unresolved 
CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.61\,$\pm$\,2.66\,\,mJy, superimposed on a 
continuum level of 4.15\,$\pm$\,0.48\,\,mJy, and a full width at half-maximum (FWHM) line width of 546\,$\pm$\,36\,\,km\,\,s\pmOne.  \par
We construct a velocity-integrated (0th moment) map of the \CO line 
emission after subtracting continuum emission in the visibility plane. This results in a velocity-integrated \CO line flux of $I_\textrm{CO}$\,=\,10.1\,$\pm$
\,1.3 Jy km\,\,s\pmOne\ over the velocity range of $\Delta v$\,$\sim$\,680 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration 
uncertainty. Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.2212\,$\pm$\,0.0010.

\begin{figure*}[tbph] 
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel.pdf}
\includegraphics[width=0.65\textwidth]{Figure/smmj0939-co32_spec.eps}
\caption{Top Left: Continuum-subtracted moment-0 map of \CO line emission toward 
the background SMG with $\sigma$\,=\,1.03\,Jy\,\,km\,\,s\pmOne\ beam\pmOne\ over a velocity range of $\Delta v$\,$\sim$\,514\,km\,\,s\pmOne. The beam size is 11$\farcs$5\,$\times$\,6\farcs2, at P.A.\,=\,$-$56\degr, as indicated in the bottom left corner. 
Top Right: Velocity-integrated \CO line emission (red contours) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14) with $\sigma_\textrm{1\,mm}$\,=\,0.84 mJy beam\pmOne. The beam size of the SMA observations is 1\farcs4$ \times $1\farcs2, P.A. $-$34\degr, as shown 
in the bottom left corner. 
The central cross on each image corresponds to the same coordinates as in Figure~\ref{fig:cont}. The contour levels start at $\pm$3$\sigma$, incrementing at
steps of $\pm$1$\sigma$. 
Bottom: 
Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$\,29 km\,\,s\pmOne\, and an rms of $\sigma_\textrm{ch}$\,=\,9.5 mJy beam\pmOne\ per channel. The
solid black line shows the Gaussian fit to the \CO line profile, and the yellow histogram shows the 
flux density as a function of velocity offset, where the velocity scale is relative to $z$\,=\,2.221. 
\label{fig:mom0}}
\end{figure*}

@@

The resulting best-fit model as shown in Figure\,\,\ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
Our best-fit model yields a magnification
factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38, this is consistent the value reported by H14 within the errors. All best-fit
parameters are listed in Table~\ref{tab:lensParam}. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1.22\,$\pm$\,0.01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0.75\,$\pm$\,0.02 (5.34\,\,kpc at $z$\,=\,0.685),
the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively. 
\input{table_lensParams}

\subsection{SED Fitting} \label{sec:SED}
\subsubsection{3C220.3}\label{sec:SEDFg}
Synchrotron continuum emission from extended components of a radio galaxy decreases with increasing radio frequencies, 
and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$, where the 
spectral index $\alpha$ is $\gtrsim$ 0.5. While the contribution from extended components decreases, studies using 
samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises 
and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}. This has been observed in a FR-II galaxy at similar redshift --- 3C220.1 at $z$ = 0.610, where observations were carried out at observed-frame $\sim$\,90 GHz \citep{Hardcastle08a}.

Previous studies of the core component of 3C220.3 have established upper 
limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a} and an unambiguous detection of 0.8 mJy at 9 GHz (H14), suggesting a substantially inverted spectrum of the core (Figure~\ref{fig:SED}).
Consequently, we may naively expect the integrated flux density in our continuum detection of $S_\textrm{104GHz}$\,=\,7.39\,$\pm$\,1.42\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685. 
However, the deconvolved spatial size of the source matching that in the resolved image (see Figure 1) is 
suggestive of a marginally resolved detection of the extended lobe components with non-negligible emission. 
This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the 
axis along the 
lobes of the radio galaxy, as shown in Figure~\ref{fig:cont}. We investigate this disparity by fitting models to 
existing SED measurements as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to 
estimate the flux density of the lobes at the frequency of our continuum measurement. 
\input{table_SED}
Following Equation (1) in \citet{Cleary07a}, the fit to the lobe emission can be expressed as a parabolic function:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending 
of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches 
unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy 
distribution. 
The extrapolated flux density at 104\,\,GHz is consistent with the peak flux density of our continuum 
measurement (Figure~\ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests
a dominant contribution from the lobes, and that the peak flux density does not correspond to emission toward 
the core. Moreover, the peak position of the 104\,\,GHz continuum is
centered toward the northern lobe (Figure~\ref{fig:cont}), which further supports our argument. We did not 
extrapolate the core measurements to the frequency of our continuum, as previous measurements of the core are 
taken 
across different epochs. 
Based on our argument, we place an upper limit of $S_\nu$\,$<$\,2.60 mJy on the core component using the difference between the integrated and the peak flux densities.
\par
Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, where some exhibit spectral steepening in cm and mm wavelengths (\eg 3C123). At the resolution of our observations, it is unclear whether the measured flux density is dominated by emission from the compact hotspot or that from the surrounding diffuse lobe components.

@@

The detection of CO in SMM\,J0939 
implies a CO luminosity of \Lp = (2.7\,$\pm$\,0.6) $\times$ 10$^{10}$ (10.1/$\mu_\textrm{L}$) \LpU, suggesting the presence of a massive 
molecular gas reservoir that fuels the star formation at a rate of $\sim$\,874\,\Msun~yr\pmOne. If the star forming activity continues at the current rate, the gas reservoir will be depleted within $\lesssim$~25 Myr, 
which is consistent with the short timescale found in SMGs \citep{Greve05a}. The derived intrinsic properties of SMM\,J0399 are evident of ongoing rapid star formation; this is in good agreement with the current conjecture that SMGs are a 
population of high-redshift galaxies that build up most of the stellar mass in the early universe, thus play an important role 
in galaxy formation and evolution (BLAH cite).

We investigate variations within the SMG population by comparing SMM\,J0939 with two other exceptionally submm-bright, 
strongly-lensed SMGs
found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which have been studied in great detail. The properties 
of these galaxies are listed in Table~\ref{tab:comapreSMG}. While the cosmic Eyelash has the least amount of molecular gas, as well as 
the 
longest gas depletion timescale (\ie long-lived), the overall gas and dust properties of SMM\,J0939 are between those of HLSW-01 and the 
cosmic
Eyelash. Such distinction is likely a result of our selection bias, while these sources appear similarly bright at 250 \micron, their lensing factors 
vary by a factor of $\sim$\,3. In particular, with the cosmic Eyelash having the highest lensing magnification among the 
three, this
intrinsically fainter, and less gas-rich SMG appears notably bright 
at 250\,\micron, with its CO line and IR luminosities lower than those of most SMGs studied to date. 
This demonstrates 
the large variations in gas mass, dust mass, thus star forming activity within the population at $z$\,$\sim$\,2, which is discernible only
 with the aid of gravitational lensing. 
While lensing can probe sources 
of various intrinsic properties, we find that SMM\,J0939 is representative of the population, with its intrinsic CO line luminosity, IR luminosity, gas mass, 
dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical", un-lensed SMGs studied to date 
\citep[\eg ][]{Greve05a,Tacconi10a}.

@@

We conclude this paper by noting that SMM\,J0939 is a faithful representation of both high-redshift type-2 quasars and SMGs, 
based on the excellent agreements found between theirs properties. In this remarkable lensing system, the background galaxy --- SMM\,J0939 is 
breaking up its dust cocoon (H14) while undergoing massive star-formation (SFR $\sim$\,874 \Msun~yr\pmOne). 
This scenario is consistent with the proposed evolutionary phase model \citep{Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.

>>>>

\begin{abstract}
We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy (SMG) SMM\,J0939+8315 at $z$ = 2.221, using  
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
The underlying continuum emission toward the foreground radio galaxy 3C220.3, at $z$ = 0.685, is detected with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy. 
Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (10.1\,$\pm$\,1.3)\,Jy\,km\,s\pmOne, we derive 
 a lensing- and excitation-corrected CO line luminosity of \Lp = (2.7\,$\pm$\,0.6) $\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling performed on the archival 1\,mm continuum emission. 
 This translates to a molecular gas mass of $M_\textrm{gas}$\,=\,(2.3\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun. 
Fitting the spectral energy distribution (SED) models to the (sub)-millimeter data of this SMG yields a rest-frame dust temperature of $T_\textrm{dust}$ = 
63.1$^{+1.1}_{-1.3}$\,K, a dust mass of $M_\textrm{dust}$ = (5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared luminosity of 
$L_\textrm{IR}$ = (9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,\Lsun, after correcting for lensing magnification.
Our comparative study 
of the intrinsic properties (\eg gas mass, dust mass, star formation rate, and surface densities) in SMM
J0939+8315 
and other high-redshift SMGs and type-2 quasars shows that SMM\,J0939+8315 is a faithful representation of both populations, suggesting that
SMM\,J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase in the currently favored evolutionary link model.
\end{abstract}
\keywords{cosmology: observations --- galaxies: formation --- galaxies: high-redshift ---  galaxies: starburst --- submillimeter: galaxies}

@@

In this paper, we present the detection of \CO line emission toward the background SMG obtained with the Combined
Array for Research in Millimeter Astronomy (CARMA), which refines the redshift, and permits the study of the physical conditions in the ISM of SMM\,J0939 in great detail. We report the detection of the underlying continuum emission and place constraints on the spectral energy distribution (SED) of the foreground FR-II galaxy at mm wavelength ($\sim$\,104 GHz). Based on the magnification factor derived from our lens model, we infer intrinsic properties of SMM\,J0939 and thereby 
conclude this paper by comparing our findings to other similarly bright, strongly-lensed SMGs, as well as other type-2 quasars at $z$\,$\sim$\,2 .

We adopt a flat $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km\,\,Mpc\pmOne\,\,s\pmOne, $\Omega_\textrm{M}$\,=\,0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
The luminosity distances at $z$\,=\,0.685 and $z$\,=\,2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
corresponds to 8.406 kpc at $z$\,=\,2.221, and 7.169 kpc at $z$\,=\,0.685.

@@

\section{Results}\label{sec:res}
%\subsection{New Results: Continuum Emission} 
\subsection{New Results: 3C220.3} 
Averaging over all line-free channels, we detect $\sim$\,9$\sigma$ continuum emission at an averaged frequency of $\nu_{cont}$\,=\,104.2106 GHz ($\sim$\,2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$\,1.7 mm) at $z$\,=\,0.685. In this lensing system, the 
foreground galaxy (3C220.3) is radio-loud, we thus expect it to be the dominant source of the continuum emission (see \S \ref{sec:SEDFg} for details). The task {\sc imfit} is used to estimate the peak position of the continuum emission, where the flux density is S$_\nu$\,=\,4.93\,$\pm$\,0.31\,\,mJy\,\,beam\pmOne. From the continuum measurement, the deconvolved source size 
is (8\farcs4\,$\pm$\,1\farcs1)\,$\times$\,(4\farcs9\,$\pm$\,0\farcs6) at $-$53.8$\degr$, and the integrated flux density is 7.39\,$\pm$\,1.42\,\,mJy. An overlay image of the 104 GHz  
continuum emission with the 9 GHz continuum emission (H14) is shown in Figure~\ref{fig:cont}, demonstrating that the continuum 
emission is marginally resolved at the resolution of our observations. It is therefore plausible that non-thermal emission from the radio lobes and core of the foreground galaxy dominate the integrated flux 
density of the measured continuum. We discuss this further in Section \ref{sec:SEDFg}. \par
The frequency range of our observations covers the HCO$^+$(2\,\rarr\,1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,\rarr\,2$_{20}$) 
transition line emission in the foreground galaxy, at 
the redshifted frequencies of 105.86, 107.71, and 108.79\,\,GHz, respectively. We establish 3$\sigma$ upper limits employing a typical FWHM line width of 
$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurements in a sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}. This results in upper limits of $<$ 2.66\,\,Jy\,\,km\,\,s\pmOne\ on the integrated emission line strengths.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel.pdf}
\caption{Left: Contour map of the 104 GHz continuum emission in the foreground radio galaxy 3C220.3. 
%The contour levels start at $\pm$2$\sigma$, where $\sigma$ = 0.5 mJy beam\pmOne, and 
%increment at steps of $\pm$2$\sigma$. 
The beam size is 12\farcs0\,$\times$\,6\farcs5, at P.A.\,=\,
$-$56$\degr$, as indicated in the bottom left corner. Right: CARMA 104 GHz continuum emission (red contours) overlaid on the VLA 9 GHz continuum emission (green contours and grayscale; H14). 
The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A. 
76$\degr$. The contour levels of the 104 GHz continuum emission start at $\pm$2$\sigma$, incrementing at steps 
of $\pm$2$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$, where $\sigma$\,=\,0.064 mJy beam\pmOne, and increment at steps of $\pm$2$^n\sigma$, 
where $n$ is a positive integer.
The central cross on each image indicates the position of the radio core of 3C220.3. \label{fig:cont}}
\end{figure*}
%\subsection{New Results: \CO Line Emission}
\subsection{New Results: SMM\,J0939\\ \CO Line Emission}
We detect \CO line emission at $\sim$\,8$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
The spatial extent of this SMG is $\sim$\,5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum in Figure~\ref{fig:mom0}; as such, 
the detected \CO line emission is spatially unresolved. We therefore extract the line profile (Figure~\ref{fig:mom0}) at the peak position of the unresolved 
CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.61\,$\pm$\,2.66\,\,mJy, superimposed on a 
continuum level of 4.15\,$\pm$\,0.48\,\,mJy, and a full width at half-maximum (FWHM) line width of 546\,$\pm$\,36\,\,km\,\,s\pmOne.  \par
We construct a velocity-integrated (0th moment) map of the \CO line 
emission after subtracting continuum emission in the visibility plane. This results in a velocity-integrated \CO line flux of $I_\textrm{CO}$\,=\,10.1\,$\pm$\,1.3 Jy km\,\,s\pmOne\ over the velocity range of $\Delta v$\,$\sim$\,680 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration 
uncertainty. Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.2212\,$\pm$\,0.0010.

\begin{figure*}[tbph] 
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel.pdf}
\includegraphics[width=0.65\textwidth]{Figure/smmj0939-co32_spec.eps}
\caption{Top Left: Continuum-subtracted moment-0 map of \CO line emission toward 
the background SMG with $\sigma$\,=\,1.03\,Jy\,\,km\,\,s\pmOne\ beam\pmOne\ over a velocity range of $\Delta v$\,$\sim$\,514\,km\,\,s\pmOne. The beam size is 11$\farcs$5\,$\times$\,6\farcs2, at P.A.\,=\,$-$56\degr, as indicated in the bottom left corner. 
Top Right: Velocity-integrated \CO line emission (red contours) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14), with an rms noise of $\sigma_\textrm{1\,mm}$\,=\,0.84 mJy beam\pmOne. The beam size of the SMA observations is 1\farcs4$ \times $1\farcs2, P.A. $-$34\degr, as shown 
in the bottom left corner. 
The central cross on each image corresponds to the same coordinates as in Figure~\ref{fig:cont}. The contour levels start at $\pm$3$\sigma$, incrementing at
steps of $\pm$1$\sigma$. 
Bottom: 
Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$\,29 km\,\,s\pmOne, and an rms of $\sigma_\textrm{ch}$\,=\,9.5 mJy beam\pmOne\ per channel. The
solid black line shows the Gaussian fit to the \CO line profile, and the yellow histogram shows the 
flux density as a function of velocity offset, where the velocity scale is relative to $z$\,=\,2.221. 
\label{fig:mom0}}
\end{figure*}

@@

The resulting best-fit model as shown in Figure\,\,\ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
Our best-fit model yields a magnification
factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38, this is consistent the value reported by H14 within the errors. All best-fit
parameters are listed in Table~\ref{tab:lensParam}. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685),
the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively. 
\input{table_lensParams}

\subsection{SED Fitting} \label{sec:SED}
\subsubsection{3C220.3}\label{sec:SEDFg}
Synchrotron continuum emission from extended components of a radio galaxy decreases with increasing radio frequencies, 
and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$, where the 
spectral index $\alpha$ is $\gtrsim$ 0.5. While the contribution from extended components decreases, studies using 
samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises 
and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}. This has been observed in a FR-II galaxy at similar redshift --- 3C220.1 at $z$ = 0.610, where observations were carried out at the observed-frame frequency of $\sim$\,90 GHz \citep{Hardcastle08a}.

Previous studies of the core component of 3C220.3 have established upper 
limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a} and an unambiguous detection of 0.8 mJy at 9 GHz (H14), suggesting a substantially inverted spectrum of the core (Figure~\ref{fig:SED}).
Consequently, we may naively expect the integrated flux density in our continuum detection of $S_\textrm{104GHz}$\,=\,7.39\,$\pm$\,1.42\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685. 
However, the deconvolved spatial size of the source matching that in the resolved image (see Figure 1) is 
suggestive of a marginally resolved detection of the extended lobe components with non-negligible emission. 
This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the 
axis along the 
lobes of the radio galaxy, as shown in Figure~\ref{fig:cont}. We investigate this disparity by fitting models to 
existing SED measurements as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to 
estimate the flux density of the lobes at the frequency of our continuum measurement. 
\input{table_SED}
Following Equation (1) in \citet{Cleary07a}, the fit to the lobe emission can be expressed as a parabolic function:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending 
of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches 
unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy 
distribution. 
The extrapolated flux density at 104\,\,GHz is consistent with the peak flux density of our continuum 
measurement (Figure~\ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests
dominant contribution from the lobes, and that the peak flux density does not correspond to emission toward 
the core. Moreover, the peak position of the 104\,\,GHz continuum is
centered toward the northern lobe (Figure~\ref{fig:cont}), which further supports our argument. We did not 
extrapolate the core measurements to the frequency of our continuum, as previous measurements of the core are 
taken 
across different epochs. 
Based on our argument, we place an upper limit of $S_\nu$\,$<$\,2.60 mJy on the core component using the difference between the integrated and the peak flux densities.
\par
Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, where some exhibit spectral steepening in cm and mm wavelengths (\eg 3C123). At the resolution of our observations, it is unclear whether the measured flux density is dominated by emission from the compact hotspot or that from the surrounding diffuse lobe components.

@@

The detection of CO in SMM\,J0939 
implies a CO luminosity of \Lp = (2.7\,$\pm$\,0.6) $\times$ 10$^{10}$ (10.1/$\mu_\textrm{L}$) \LpU, suggesting the presence of a massive 
molecular gas reservoir that fuels the star formation at a rate of $\sim$\,874 \Msun~yr\pmOne. If the star forming activity continues at the current rate, the gas reservoir will be depleted within $\lesssim$~25 Myr, 
which is consistent with the short timescale found in SMGs \citep{Greve05a}. The derived intrinsic properties of SMM\,J0399 are evident of ongoing rapid star formation; this is in good agreement with the current conjecture that SMGs are a 
population of high-redshift galaxies that build up most of the stellar mass in the early universe, thus play an important role 
in galaxy formation and evolution \citep[\eg ][]{Micha10a}.

We investigate variations within the SMG population by comparing SMM\,J0939 with two other exceptionally submm-bright, 
strongly-lensed SMGs
found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which have been studied in great detail. The properties 
of these galaxies are listed in Table~\ref{tab:comapreSMG}. While the cosmic Eyelash has the least amount of molecular gas, as well as 
the 
longest gas depletion timescale (\ie long-lived), the overall gas and dust properties of SMM\,J0939 are between those of HLSW-01 and the 
cosmic
Eyelash. Such distinction is likely a result of our selection bias, while these sources appear similarly bright at 250 \micron, their lensing factors 
vary by a factor of $\sim$\,3. In particular, with the cosmic Eyelash having the highest lensing magnification among the 
three, this
intrinsically fainter, and less gas-rich SMG appears notably bright 
at 250\,\micron, with its CO line and IR luminosities lower than those of most SMGs studied to date. 
This demonstrates 
the large variations in gas mass, dust mass, thus star forming activity within the population at $z$\,$\sim$\,2, which is discernible only
 with the aid of gravitational lensing. 
While lensing can probe sources 
of various intrinsic properties, we find that SMM\,J0939 is representative of the population, with its intrinsic CO line luminosity, IR luminosity, gas mass, 
dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical" SMGs studied to date 
\citep[\eg ][]{Greve05a,Tacconi10a}.

@@

We conclude this paper by noting that SMM\,J0939 is a faithful representation of both high-redshift type-2 quasars and SMGs, 
based on the excellent agreements found between theirs properties. In this remarkable lensing system, the background galaxy --- SMM\,J0939 is 
breaking up its dust cocoon (H14) while undergoing prodigious star-formation (SFR\,$\sim$\,874 \Msun~yr\pmOne). 
This scenario is consistent with the proposed evolutionary phase model \citep{Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.
